Can Communication Protocols Find Small LPs?

### 2019-04-05 CS860-CommunicationComplexity/project/presentation.tex

\usepackage{tikz}
\title{Communication Complexity of Knapsack Cover}
\subtitle{CCFest}
% \date{\today}
\date{}
\author{By W. Justin Toth}
\institute{CS860 - Communication Complexity}
\titlegraphic{\hfill\includegraphics[height=1.5cm]{logo.png}}

@@

\begin{document}

\maketitle

\begin{frame}{A First Slide}
\end{frame}
\end{document}

>>>>

\usepackage{tikz}
\title{Can Communication Protocols Find Small LPs?}
\subtitle{Knapsack Cover, Extended Formulations, and Communication Complexity}
% \date{\today}
\date{}
\author{By W. Justin Toth}
\institute{CS860 - Communication Complexity}
\titlegraphic{\hfill\includegraphics[height=1.5cm]{logo.png}}

@@

\begin{document}
\setbeamercolor{background canvas}{bg=white}
\maketitle

\begin{frame}{The Min Knapsack Problem}
Given $n$ items with individual sizes, $s_i$, and costs, $c_i$, for $i \in [n]$.
\vfill
Also given a demand $D$. Want to compute the \alert{Min Knapsack}

\begin{align*}
\min\ &\sum_{i\in [n]} c_i x_i \\
\text{s.t.} &\sum_{i \in [n]} s_i x_i \geq D \\
&x \in \{0,1\}^n.
\end{align*}
\vfill
Standard Linear Programming relaxation has an unbounded integrality gap.
\end{frame}
\begin{frame}{Knapsack Cover Inequalities}
LP relaxation can be strengthened to an integrality gap of $2$ via all Knapsack Cover Inequalities.
\vfill
Knapsack Cover Inequality for $B\subseteq [n]$ is the inequality of the form 
$$\sum_{i \in [n]\backslash B} s_i(B) x_i \geq D(B),$$
where $D(B) = \max\{D-\sum_{i\in B} s_i, 0\}$ and $s_i(B) = \min\{s_i, D(B)\}.$
\vfill
\textbf{Big Open Question:} Is there a polynomial size formulation for Knapsack Cover LP?
\end{frame}
\begin{frame}{Extended Formulations}
    \begin{columns}
        \begin{column}{0.5\textwidth}
    \begin{figure}
        \includegraphics[scale=0.075]{std_ex.png}
    \end{figure}
\end{column}
\begin{column}{0.5\textwidth}
\textbf{Extension Complexity:} Min number of facets to describe a polytope as the projection of a higher dimensional polyhedron.
\end{column}
\end{columns}
\end{frame}
\begin{frame}{Communication Protocols for the Slack Matrix}
\end{frame}
\begin{frame}{Results}
\end{frame}
\end{document}
